### 2022-11-30 abstract.tex
some fixes

The first and largest part of this thesis extends a recently proposed
reverse-Bayes method for quantifying replication success. The key idea is to
challenge the finding from the original study with a sceptical prior so that the
resulting posterior provides no longer evidence for the finding from the study.
While the original proposal defined evidence through tail probabilities, the
extension developed here replaces them with Bayes
factors. % The sceptical prior is now
% determined such that the original finding is no longer convincing in terms of a
% Bayes factor. In contrast to tail probabilities,
We find that the extended method combines two notions of replicability: It
ensures that original and replication study independently provide evidence for
an effect while also ensuring that their effect estimates are compatible.
Compared to the original method, the extension also avoids a statistical paradox
which the original method suffered from.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
The second extensions recalibrates the original procedure to produce more
appropriate inferences in terms of effect size. % from the relative effect size
% perspective
The recalibration is chosen such that for borderline significant original
studies, replication success can only be achieved if the replication effect
estimate is larger than the original one. The recalibrated procedure has good
frequentist properties comparable to the standard method used in practice. The
third extension provides a framework for Bayesian design of replication studies
which allows for combining the data from the original study with external
knowledge. External knowledge, such as data from other studies, is ubiquitous in
the replication setting and it can potentially lead to more efficient designs
compared to classical approaches that cannot take it into account.

The second part of the thesis is concerned with reverse-Bayes approaches in
general. The reverse-Bayes idea was first proposed in the 1950s, but it has
mostly been forgotten. To increase awareness and show potential use cases,
reverse-Bayes history and methods are summarized in a comprehensive review. The
review includes also some new results on connections between revere-Bayes
methods and meta-analysis. Finally, a commentary paper on a recently proposed
reverse-Bayes method draws connections to other reverse-Bayes methods.

The last part of the thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for the low replicability in
applied research. These practices can similarly harm methodological research,
but this is often not recognized. To raise awareness, an illustrative simulation
study is conducted in which it is shown how a novel method can easily be
presented as superior over established competitor methods if questionable
research practices are employed.

>>>>

The first and largest part of this thesis extends a recently proposed
reverse-Bayes method for quantifying replication success. The key idea is to
challenge the data from the original study with a sceptical prior so that the
resulting posterior no longer provides evidence for the finding from the study.
While the proposed method defined evidence through tail probabilities, the
extension developed here replaces them with Bayes
factors. % The sceptical prior is now
% determined such that the original finding is no longer convincing in terms of a
% Bayes factor. In contrast to tail probabilities,
We find that the extended method combines two notions of replicability: It
requires that original and replication study independently provide evidence for
an effect and ensures that their effect estimates are compatible. The extended
method also avoids a statistical paradox which the proposed method suffered
from.
% Bayes factors have a more
% natural interpretation and allow for direct quantification of evidence for one
% hypothesis versus another. As with the sceptical $p$-value, the procedure leads
% to a single measure quantifying the degree of replication success called the
% sceptical Bayes factor.
Another extension proposed in this thesis recalibrates the proposed method to
produce more appropriate inferences in terms of effect
size. % from the relative effect size
% perspective
The recalibration is chosen such that for original studies which were borderline
significant, replication success can only be achieved if the replication effect
estimate is larger than the original one. The recalibrated method has good
frequentist properties comparable to standard methods used in practice. The
third and last extension provides a framework for Bayesian design of replication
studies which allows for combining data from the original study with external
knowledge. External knowledge, such as data from other studies, is ubiquitous in
the replication setting and taking it into account can potentially lead to more
efficient designs compared to classical approaches.

The second part of the thesis is concerned with reverse-Bayes methodology. The
reverse-Bayes idea was first proposed in the 1950s, but it has mostly been
forgotten. To increase awareness and show potential use cases, reverse-Bayes
history and methods are summarized in a comprehensive review. The review
includes also some new results on connections between revere-Bayes methods and
meta-analysis. Finally, a commentary paper on a recently proposed reverse-Bayes
method draws connections to other reverse-Bayes methods.

The last part of the thesis revolves around research integrity issues in
methodological research. Questionable research practices, such as selective
reporting of results, are often seen as main cause for the low replicability in
applied research. These practices can similarly harm methodological research,
but are often not recognized. To raise awareness, an illustrative simulation
study is conducted in which it is shown how a novel method can easily be
presented as superior over established competitor methods if questionable
research practices are employed.
